Schramm-Loewner evolution in tricritical Ising model

### 2013-05-06 AffineLieAlgebras/Simons/tricritical-ising-sle.tex
Some notes for tricritical Ising

>>>>

Tricritical Ising: integrability (RSOS), supersymmetry (?), conformally-invariant boundary conditions, identification with CFT. 
CFT with supersymmetry (additional generators and relations). 
Boundary conditions, CFT primary fields and SLE. 
SLE on superspace \cite{nagi2005stochastic,rasmussen2004stochastic} and BCFT for tricritical Ising (parameter correspondence).

Proof: discrete holomorphicity and integrability. 
(Loop description?)
\bibliography{bibliography}{} 
\bibliographystyle{utphys}
